---
title: "SeedlingStudy"
author: "Samantha Brown"
date: "4/16/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the packages

We are loading PhotoSynq Data.

Tidyverse ia an umberlla library which has utilities to read csv files, do file manipulations and plotting

```{r}
library(ggplot2)
library(readr)
library(magrittr)
library(lubridate)
```

## Load the data files


```{r, echo=FALSE}
microclimate_photosynq <- read_csv('./data/microclimate_photosynq_data.csv')
summary(microclimate_photosynq)
```

## Exploratory plots

Exploring relationships between variables. But, lets first format the required colums so that they are plot/analysis ready

```{r, echo=FALSE}
head(microclimate_photosynq)
microclimate_photosynq$localdate <- mdy(microclimate_photosynq$Date)
microclimate_photosynq$localdatetime  <- ymd_hms(paste(microclimate_photosynq$localdate,microclimate_photosynq$Time,sep = ' '))

```

## Temp/Humidity for the days of experiment

```{r, echo=FALSE}
microclimate_photosynq %>% ggplot(aes(x=localdatetime,y=`Ambient Temperature`)) + geom_point() +
  labs(x="Time (Date)", y="Ambient Temperature (deg C)")

```

```{r, echo=FALSE}
microclimate_photosynq %>% ggplot(aes(x=localdatetime,y=`Ambient Humidity`)) + geom_point() +
  labs(x="Time (Date)", y="Ambient Humidity (deg C)")

```

## Are there elevational differences in PSystem 2 (proxy of Photosynthetic capacity) for both the species? 

```{r, echo=FALSE}
microclimate_photosynq %>% ggplot() + geom_bar(aes(x=Species,y=Phi2),stat = "identity") + facet_grid(.~Stand) +
  labs(x="Species",y="PS2 (units ??)") + theme_minimal(base_size = 12)
ggsave(filename = "figs/Species-comparisions.png",dpi = 300, width = 4, height = 4, units = "in")
```

I see ....

```{r, echo=FALSE}
microclimate_photosynq %>% ggplot() + geom_bar(aes(x=Species,y=`Light Intensity (PAR)`),stat = "identity") + facet_grid(.~Stand) +
  labs(x="Species",y="PAR (units ??)") + theme_minimal(base_size = 12)
ggsave(filename = "figs/Species-comparisions-lightPAR.png",dpi = 300, width = 4, height = 4, units = "in")
```

I see PAR pattern....

## Are there elevational differences in PSystem 2 (proxy of Photosynthetic capacity) for both the species? Is it statiscally significant

Lets do t-test to figure out if therer is any differences in PS2 of WH and PSF - Null Hypothesis -> No diff
```{r, echo=FALSE}
t.test(microclimate_photosynq[microclimate_photosynq$Species=='ABAM',c('Phi2')]$Phi2,
       microclimate_photosynq[microclimate_photosynq$Species=='TSHE',c('Phi2')]$Phi2)
```
