---
title: "SeedlingStudy"
author: "Samantha Brown"
date: "4/16/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the packages

We are loading PhotoSynq Data.

Tidyverse ia an umberlla library which has utilities to read csv files, do file manipulations and plotting

```{r}
library(ggplot2)
library(readr)
library(magrittr)
library(lubridate)
library(tidyverse)
```

## Load the data files


```{r, echo=FALSE}
photosynq.data <- read_csv('./data/photosynq.csv')
photosynq <- photosynq.data[!photosynq.data$Phi2 == "0.136", ]
summary(photosynq)
```

## Exploratory plots

Exploring relationships between variables. But, lets first format the required colums so that they are plot/analysis ready

```{r, echo=FALSE}
head(photosynq)
photosynq$localdate <- mdy(photosynq$Date)
photosynq$localdatetime  <- ymd_hms(paste(photosynq$localdate,photosynq$Time,sep = ' '))

```

## Temp/Humidity for the days of experiment

```{r, echo=FALSE}
photosynq %>% ggplot(aes(x=localdatetime,y=`Temperature`)) + geom_point() +
  labs(x="Time (Date)", y="Ambient Temperature (deg C)")

```

```{r, echo=FALSE}
photosynq %>% ggplot(aes(x=localdatetime,y=`Humidity`)) + geom_point() +
  labs(x="Time (Date)", y="Ambient Humidity (deg C)")

```

## Are there elevational differences in PSystem 2 (proxy of Photosynthetic capacity) for both the species? 

```{r, echo=FALSE}
photosynq %>% ggplot() + geom_bar(aes(x=Species,y=Phi2),stat = "summary", fun.y = "mean") + facet_grid(.~Stand) +
  labs(x="Species",y="PS2") + theme_minimal(base_size = 12)
ggsave(filename = "figs/Species-comparisions.png",dpi = 300, width = 4, height = 4, units = "in")
```

There seem to be similar patterns of ABAM having higher photosyem II quantum yield than TSHE for both elevations.

```{r, echo=FALSE}
photosynq %>% ggplot() + geom_bar(aes(x=Species,y='PAR'),stat = "summary", fun.y = "mean") + facet_grid(.~Stand) +
  labs(x="Species",y="PAR") + theme_minimal(base_size = 12)
ggsave(filename = "figs/Species-comparisions-lightPAR.png",dpi = 300, width = 4, height = 4, units = "in")
```

There seem to be similar patterns of ABAM experiencing more light radiation than TSHE at both elevations. This is consistant with the assumption that TSHE is more shade tolerant, and thus can outcompete ABAM where there is less light available.

## Are there elevational differences in PSystem 2 (proxy of Photosynthetic capacity) for both the species? Is it statiscally significant?

Lets do t-test to figure out if there are any differences in PS2 of TSHE and ABAM - Null Hypothesis -> No diff
```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM',c('Phi2')]$Phi2,
       photosynq[photosynq$Species=='TSHE',c('Phi2')]$Phi2)
t.test(photosynq[photosynq$Stand=='TO04',c('Phi2')]$Phi2,
       photosynq[photosynq$Stand=='AV06',c('Phi2')]$Phi2)
t.test(photosynq[photosynq$Station=='CN01',c('Phi2')]$Phi2,
       photosynq[photosynq$Station=='TN01',c('Phi2')]$Phi2)

```
There is a statistically significant difference in photosystem 2 quantum yield between species and  elevation but not between canopy coverage.

Now I will try comparing a parameter that measures plant stress (NPQ).
```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM',c('NPQt')]$NPQt,
       photosynq[photosynq$Species=='TSHE',c('NPQt')]$NPQt)
t.test(photosynq[photosynq$Stand=='TO04',c('NPQt')]$NPQt,
       photosynq[photosynq$Stand=='AV06',c('NPQt')]$NPQt)
t.test(photosynq[photosynq$Station=='CN01',c('NPQt')]$NPQt,
       photosynq[photosynq$Station=='TN01',c('NPQt')]$NPQt)
```
nonphotochemical quenching is higher for TSHE than ABAM and for AV06 than TO04

```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM',c('PAR')]$PAR,
       photosynq[photosynq$Species=='TSHE',c('PAR')]$PAR)
t.test(photosynq[photosynq$Stand=='TO04',c('PAR')]$PAR,
       photosynq[photosynq$Stand=='AV06',c('PAR')]$PAR)
t.test(photosynq[photosynq$Station=='CN01',c('PAR')]$PAR,
       photosynq[photosynq$Station=='TN01',c('PAR')]$PAR)
```
There is significantly higher light radiation for gaps than nongaps and for TSHE than ABAM.

```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01',c('PAR')]$PAR)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01',c('PAR')]$PAR)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='TO04',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='TO04',c('PAR')]$PAR)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='AV06',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='AV06',c('PAR')]$PAR)
```
ABAM has lower PAR than TSHE. This is statistically significant at stand TO04 and stations TN01 and CN01.

Now I will look at the PAR for each species between stations (gap/nogap) at TO04 and AV06.

```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01' & photosynq$Stand=='TO04',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01' & photosynq$Stand=='TO04',c('PAR')]$PAR)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01' & photosynq$Stand=='TO04',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01' & photosynq$Stand=='TO04',c('PAR')]$PAR)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01' & photosynq$Stand=='AV06',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01' & photosynq$Stand=='AV06',c('PAR')]$PAR)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01' & photosynq$Stand=='AV06',c('PAR')]$PAR,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01' & photosynq$Stand=='AV06',c('PAR')]$PAR)
```
TSHE having higher PAR than ABAM at the stand TO04(lower elevation) is only at the station TN01(nogap/shaded).
```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM',c('Temperature')]$Temperature,
       photosynq[photosynq$Species=='TSHE',c('Temperature')]$Temperature)
t.test(photosynq[photosynq$Stand=='TO04',c('Temperature')]$Temperature,
       photosynq[photosynq$Stand=='AV06',c('Temperature')]$Temperature)
t.test(photosynq[photosynq$Station=='CN01',c('Temperature')]$Temperature,
       photosynq[photosynq$Station=='TN01',c('Temperature')]$Temperature)
```
There is no trend for temperature and species, but there is statisically significantly higher temperatures at TO04 than AV06 (lower elevation = higher temperature) and at CN01 than TN01 (canopy gap = higher temperature)

Higher temperature and light radiation meet the expectations for canopy gaps compared to closed canopies.

Now I will see if the difference in radiation and temperature correspond with photosytem II activity.
```{r, echo=FALSE}
model_linear1 <- lm(Phi2 ~ PAR, data = photosynq)
summary(model_linear1)
PAR_Phi2_intercept <- coef(model_linear1)[1]
PAR_Phi2_slope <- coef(model_linear1)[2]
```
R squared is very low, I would like to try creating linear regressions with a subset of the values, so I can see the relantionship when filtered by species/elevation/canopy coverage.

```{r, echo=FALSE}
ggplot(data = photosynq, aes(x=PAR,y=Phi2)) + geom_point() +
  labs(x="PAR", y="Yield of Photosystem 2") + geom_abline(intercept = PAR_Phi2_intercept, slope = PAR_Phi2_slope, color = 'red')
```

```{r, echo=FALSE}
model_linear2 <- lm(Phi2 ~ Temperature, data = photosynq[photosynq$Species=="ABAM",])
summary(model_linear2)
Temperature_Phi2_intercept <- coef(model_linear2)[1]
Temperature_Phi2_slope <- coef(model_linear2)[2]
```
```{r, echo=FALSE}
model_linear2 <- lm(Phi2 ~ Temperature, data = photosynq[photosynq$Species=="TSHE",])
summary(model_linear2)
Temperature_Phi2_intercept <- coef(model_linear2)[1]
Temperature_Phi2_slope <- coef(model_linear2)[2]
```
R squared value is also very low here.

```{r, echo=FALSE}
ggplot(data = photosynq, aes(x=Temperature,y=Phi2)) + geom_point() +
  labs(x="Temperature(C)", y="Yield of Photosystem 2") + geom_abline(intercept = Temperature_Phi2_intercept, slope = Temperature_Phi2_slope, color = 'red') + facet_grid(.~Species)
```
```{r, echo=FALSE}
model_linear3 <- lm(Phi2 ~ PAR, data = photosynq)
summary(model_linear3)
PAR_Phi2_intercept <- coef(model_linear3)[1]
PAR_Phi2_slope <- coef(model_linear3)[2]
```

```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01',c('NPQt')]$NPQt,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01',c('NPQt')]$NPQt)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01',c('NPQt')]$NPQt,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01',c('NPQt')]$NPQt)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='TO04',c('NPQt')]$NPQt,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='TO04',c('NPQt')]$NPQt)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='AV06',c('NPQt')]$NPQt,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='AV06',c('NPQt')]$NPQt)

```
in gaps: TSHE more stressed than ABAM
at high elevation: TSHE more stressed than ABAM

Now to see the other parameter of stress (PhiNO).
```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01',c('PhiNO')]$PhiNO)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01',c('PhiNO')]$PhiNO)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='TO04',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='TO04',c('PhiNO')]$PhiNO)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='AV06',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='AV06',c('PhiNO')]$PhiNO)
```
ABAM at high elevation has a higher amount of light energy going towards non-regulated processes indicating stress. This is not in line with the results for PhiNPQ.
```{r, echo=FALSE}
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01',]$LEF,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01',]$LEF)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01',]$LEF,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01',]$LEF)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='TO04',]$LEF,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='TO04',]$LEF)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='AV06',]$LEF,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='AV06',]$LEF)

```
LEF is higher for TSHE than ABAM at low elevation

```{r}
## ABAM vs. TSHE for gap low elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01' & photosynq$Stand=='TO04',c('Chlorophyll')]$Chlorophyll,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01' & photosynq$Stand=='TO04',c('Chlorophyll')]$Chlorophyll)
## ABAM vs. TSHE for nogap low elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01' & photosynq$Stand=='TO04',c('Chlorophyll')]$Chlorophyll,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01' & photosynq$Stand=='TO04',c('Chlorophyll')]$Chlorophyll)
## ABAM vs. TSHE for gap high elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01' & photosynq$Stand=='AV06',c('Chlorophyll')]$Chlorophyll,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01' & photosynq$Stand=='AV06',c('Chlorophyll')]$Chlorophyll)
## ABAM vs. TSHE for nogap high elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01' & photosynq$Stand=='AV06',c('Chlorophyll')]$Chlorophyll,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01' & photosynq$Stand=='AV06',c('Chlorophyll')]$Chlorophyll)

```
ABAM has higher chrlorphyll content at no gap low elevation and high elevation gap.
```{r}
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01',]$Phi2)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01',]$Phi2,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01',]$Phi2)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='TO04',]$Phi2,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='TO04',]$Phi2)
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Stand=='AV06',]$Phi2,
photosynq[photosynq$Species=='TSHE' & photosynq$Stand=='AV06',]$Phi2)

```

ABAM higher Phi2 than TSHE under all conditions
```{r}
##compare gaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$Phi2)
##compare nogaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$Phi2)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$Phi2)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$Phi2)
```
```{r}
##compare gaps between stands for TSHE
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01' & photosynq$Species=='TSHE',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01' & photosynq$Species=='TSHE',]$Phi2)
##compare nogaps between stands for TSHE
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01' & photosynq$Species=='TSHE',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01' & photosynq$Species=='TSHE',]$Phi2)
##compare gaps vs nongaps at the same stand for TSHE
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01' & photosynq$Species=='TSHE',]$Phi2,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01' & photosynq$Species=='TSHE',]$Phi2)
##compare gaps vs nongaps at the same stand for TSHE
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01' & photosynq$Species=='TSHE',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01' & photosynq$Species=='TSHE',]$Phi2)
```
only significant - TO04 CN01 higher Phi2 than AV06 CN01 for TSHE

```{r}
##compare gaps between stands for ABAM
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01' & photosynq$Species=='ABAM',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01' & photosynq$Species=='ABAM',]$Phi2)
##compare nogaps between stands for ABAM
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01' & photosynq$Species=='ABAM',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01' & photosynq$Species=='ABAM',]$Phi2)
##compare gaps vs nongaps at the same stand for ABAM
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01' & photosynq$Species=='ABAM',]$Phi2,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01' & photosynq$Species=='ABAM',]$Phi2)
##compare gaps vs nongaps at the same stand for ABAM
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01' & photosynq$Species=='ABAM',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01' & photosynq$Species=='ABAM',]$Phi2)

```
```{r}
## ABAM vs. TSHE for gap low elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01' & photosynq$Stand=='TO04',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01' & photosynq$Stand=='TO04',c('PhiNO')]$PhiNO)
## ABAM vs. TSHE for nogap low elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01' & photosynq$Stand=='TO04',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01' & photosynq$Stand=='TO04',c('PhiNO')]$PhiNO)
## ABAM vs. TSHE for gap high elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='CN01' & photosynq$Stand=='AV06',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='CN01' & photosynq$Stand=='AV06',c('PhiNO')]$PhiNO)
## ABAM vs. TSHE for nogap high elevation
t.test(photosynq[photosynq$Species=='ABAM' & photosynq$Station=='TN01' & photosynq$Stand=='AV06',c('PhiNO')]$PhiNO,
photosynq[photosynq$Species=='TSHE' & photosynq$Station=='TN01' & photosynq$Stand=='AV06',c('PhiNO')]$PhiNO)
```

```{r}
##compare gaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$Phi2)
##compare nogaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$Phi2)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$Phi2)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$Phi2)
```
low elevation more PS going on
```{r, echo=FALSE}
##compare gaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$PhiNPQ,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$PhiNPQ)
##compare nogaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$PhiNPQ,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$PhiNPQ)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$PhiNPQ,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$PhiNPQ)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$PhiNPQ,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$PhiNPQ)
```
high elevation more stress than low in gaps
```{r, echo=FALSE}
##compare gaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$PAR,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$PAR)
##compare nogaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$PAR,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$PAR)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$PAR,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$PAR)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$PAR,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$PAR)
```
Gap high elevation higher PAR than low elevation
No gap low elevation higher PAR than high elevation
At high elevation gap > nongap PAR
```{r, echo=FALSE}
##compare gaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$Humidity,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$Humidity)
##compare nogaps between stands
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$Humidity,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$Humidity)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Station=='CN01',]$Humidity,
photosynq[photosynq$Stand=='TO04' & photosynq$Station=='TN01',]$Humidity)
##compare gaps vs nongaps at the same stand
t.test(photosynq[photosynq$Stand=='AV06' & photosynq$Station=='CN01',]$Humidity,
photosynq[photosynq$Stand=='AV06' & photosynq$Station=='TN01',]$Humidity)
```
```{r}
t.test(photosynq[photosynq$Stand=='TO04' & photosynq$Species=='ABAM',]$Phi2,
photosynq[photosynq$Stand=='AV06' & photosynq$Species=='TSHE',]$Phi2)
```
```{r, echo=FALSE}
photosynq %>% ggplot() + geom_bar(aes(x=Species,y='Phi2'),stat = "summary", fun.y = "mean") + facet_grid(.~Station) +
  labs(x="Species",y="Phi2") + theme_minimal(base_size = 12)
ggsave(filename = "figs/Species-comparisions-Phi2.png",dpi = 300, width = 4, height = 4, units = "in")
```
```{r, echo=FALSE}
photosynq %>% ggplot() + geom_bar(aes(x=Stand,y='Phi2'),stat = "summary", fun.y = "mean") +
  labs(x="Stand",y="Phi2") + theme_minimal(base_size = 12)
ggsave(filename = "figs/Stand-comparisons-Phi2.png",dpi = 300, width = 4, height = 4, units = "in")
```